Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-07-31 paper.tex

Multiple reads are shown in Algorithm~\ref{algo:multiple-reads}.  The
main idea of this algorithm is that blocks are read partially (line 9)
to ensure that the memory buffer only contains contiguous bytes, at
any time. Therefore, the buffer can be written continuously to the
reconstructed image, without seeking (line 13).  It should be noted
that a given block might be read multiple times, in different memory
loads. 
\begin{algorithm}[h]
  \caption{Buffered merging of blocks with multiple reads}
  \label{algo:multiple-reads}
  \begin{algorithmic}[1]
  \STATE sorted\_splits = sort splits by increasing (z,y,x) values
  \STATE start\_index = 0 ; end\_index=(m-1)
  \STATE write\_range = (start\_index, end\_index)
  \WHILE{end\_index \textless Rb}
    \STATE initialize buffer
    \FOR{split in sorted\_splits}
      \IF{split has voxels in write\_range}
        \STATE split\_data = read split
        \STATE in split\_data, extract the rows in write\_range
        \STATE write rows to buffer
      \ENDIF
    \ENDFOR
    \STATE write buffer to reconstructed\_image
    \STATE start\_index = end\_index + 1
    \STATE end\_index += m
  \ENDWHILE

@@

For simplicity, we assume that $m'$ represents an integer number $k$
of block rows (case 1, $k<\sqrt[3]{n}$), of complete rows (case 2,
$k<d$), of tile rows (case 3, $k<\sqrt[3]{n}$), of slices (case 4,
$k<d$) or of block slices (case 5, $k<\sqrt[3]{n}$) \todo{make a
  figure}. In each of these 5 cases, we define $v$ as follows:
\begin{equation*}
  v_1=db \text{ ; }  v_2=Db \text{ ; } v_3=Ddb \text{ ; } v_4=D^2b \text{ ; } v_5=D^2db
\end{equation*}
so that we have:
\begin{equation*}
k_i=\floor*{\frac{m}{v_i}} \quad \mathrm{and} \quad m_i'=k_iv_i, \quad i \in \llbracket 1,5 \rrbracket
\end{equation*}

>>>>

Multiple reads are shown in Algorithm~\ref{algo:multiple-reads}.  The
main idea of this algorithm is that blocks are read partially (line 9)
to ensure that the memory buffer only contains contiguous bytes, at
any time. Therefore, the buffer can be written continuously to the
reconstructed image, without seeking (line 13).  It should be noted
that a given block might be read multiple times, in different memory
loads.

\begin{figure}
\centering
\def\svgwidth{0.3\columnwidth}
\input{figures/svg/mreads-case1.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/svg/mreads-case2.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/svg/mreads-case3.pdf_tex}

\medskip

\def\svgwidth{0.3\columnwidth}
\input{figures/svg/mreads-case4.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/svg/mreads-case5.pdf_tex}
\caption{Memory-load configurations in multiple reads, leading to
  different number of seeks. Red regions shows different memory
  load in each case. Small dots are used to represent block frontiers,
  long dashes used to represent rows/slices in blocks.}
\label{fig:multiple-reads-cases}
\end{figure}

\begin{algorithm}[h]
  \caption{Buffered merging of blocks with multiple reads}
  \label{algo:multiple-reads}
  \begin{algorithmic}[1]
  \STATE sorted\_splits = sort splits by increasing (z,y,x) values
  \STATE start\_index = 0 ; end\_index=(m-1)
  \STATE write\_range = (start\_index, end\_index)
  \WHILE{end\_index \textless Rb}
    \STATE initialize buffer
    \FOR{split in sorted\_splits}
      \IF{split has voxels in write\_range}
        \STATE split\_data = read split
        \STATE in split\_data, extract the rows in write\_range
        \STATE write rows to buffer
      \ENDIF
    \ENDFOR
    \STATE write buffer to reconstructed\_image
    \STATE start\_index = end\_index + 1
    \STATE end\_index += m
  \ENDWHILE

@@

For simplicity, we assume that $m'$ represents an integer number $k$
of block rows (case 1, $k<\sqrt[3]{n}$), of complete rows (case 2,
$k<d$), of tile rows (case 3, $k<\sqrt[3]{n}$), of slices (case 4,
$k<d$) or of block slices (case 5, $k<\sqrt[3]{n}$) \todo{make a
  figure}. In each of these 5 cases in Figure~\ref{fig:multiple-reads-cases}, we define $v$ as follows:
\begin{equation*}
  v_1=db \text{ ; }  v_2=Db \text{ ; } v_3=Ddb \text{ ; } v_4=D^2b \text{ ; } v_5=D^2db
\end{equation*}
so that we have:
\begin{equation*}
k_i=\floor*{\frac{m}{v_i}} \quad \mathrm{and} \quad m_i'=k_iv_i, \quad i \in \llbracket 1,5 \rrbracket
\end{equation*}
